Analytics without Tuning Considered Harmful?\\(Two Case Studies in Defect Prediction)

### 2015-02-19 tuningpredictor.tex
typo

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Analytics without Tuning Considered Harmful?\\(Two Case Studies in Defect Prediction)}
\numberofauthors{1}
\author{
\alignauthor
Wei Fung, TimMenzies\\
       \affaddr{Computer Science, North Carolina State University, USA}\\
       {wfu@ncsu.edu, tim.menzies@gmail.com}}

@@

and we reflect on that model, are we

>>>>

\conferenceinfo{FSE}{'15 Bergamo, Italy}
\title{Analytics without Tuning Considered Harmful?\\(Two Case Studies in Defect Prediction)}
\numberofauthors{1}
\author{
\alignauthor
Wei Fung, Tim Menzies\\
       \affaddr{Computer Science, North Carolina State University, USA}\\
       {wfu@ncsu.edu, tim.menzies@gmail.com}}

@@

good news:
\bi 
\item Tuning is easy (but one measure, at least an order of magnitude easier than 
standard optimization problems)
\item Tuning can dramatically improve the performance of a learner (in one case, from recalls
of zero to 70\%)
\ei
interesting news
\bi 
\item tunings different for different data sets.
\ei 
bad news:
\bi
\item Tuning also changes what was learned
\bi
\item Supposedly ``bad'' learners start working much better than supposedly ``best'' learners;
\item The models used in the tuned models were very different to those used in the untuned learners.
\ei 
\ei 
and we reflect on that model, are we
